ESRC SDAI Application

### 2019-06-19 case_for_support.tex
Anna update

\textbf{Aim 1.} First, using the CSEW data, we will conduct a statistical analysis to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation. We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, and the type of abuse suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.

@@

\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these. For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse.

Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse. Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases. \textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level}.

>>>>

\textbf{Aim 1.} First, using the CSEW data, we will conduct a statistical analysis to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation. We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, and the type of abuse suffered (physical abuse, threats, sexual abuse). The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables. \textit{Could we also use a e.g. a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW. We are particularly interested in the association between experiences of domestic abuse and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.

@@

\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, but the question has not been explored in a UK context yet. Our rich data allows us to determine the relative explanatory power of these. For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse through reduced collective efficacy. Another potential pathway is social norms, suggesting that acceptance and normalisation of violence within a community can encourage domestic abuse. Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse. Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases. Using a spatial regression will account for the spatial dependency between our observations and improve the reliability of our estimates. \textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?}.
